%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD in Computer Science (Ongoing)} % Degree
    {Western Norway University of Applied Sciences} % Institution
    {Sogndal and Bergen, Norway} % Location
    {Jan. 2023 -} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Ongoing PhD in Computer Science. Main area of focus is computer vision and object detection.}
      \end{cvitems}
    }

  \cventry
    {M.Sc in Computer Science - Data Science} % Degree
    {University of Stavanger} % Institution
    {Stavanger, Norway} % Location
    {Aug. 2020 - Jun. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Engineering degree in Computer Science with specialisation in Data Science.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Exchange Semester} % Degree
    {Uppsala University} % Institution
    {Uppsala, Sweden} % Location
    {Aug. 2021 - Jan. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Elective courses in computer science with specialisation in data science, stochastic machine learning, databases II and image analysis.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {B.E. in Computer Science} % Degree
    {Norwegian University of Science and Tecgnology} % Institution
    {Gjøvik, Norway} % Location
    {Jun. 2017 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Engineering degree in computer science. Elective courses were Mathematics 3, Infrastructure as Code and Introduction to Artificial Intelligence.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Certificate of Apprenticeship: Computer Technician} % Degree
    {Sogn og Fjordane County Municipality} % Institution
    {Leikanger, Norway} % Location
    {Aug. 2015 - Jan. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Apprenticeship at the Sogn og Fjordane County Municipality.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
