%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
    {Summer Internship / Researcher / PhD Student} % Job title
    {Western Norway Research Institute} % Organization
    {Sogndal, Norway} % Location
    {Jun. 2021 - today} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Research Intern summer of 2021. Participated in Teknoløft Sogn og Fjordane with an aim of identifying data science applications in the region.}
        \item {Masters Thesis: Fairness and Interpretability in Machine Learning written together with University of Stavanger and Western Norway Research Institute.}
        \item {Full Time employee as of August 2022 working as a researcher in Teknoløft Sogn og Fjordane.}
        \item {PhD Student as of January 2023.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Summer Internship} % Job title
    {Norwegian Digitalisation Agency} % Organization
    {Leikanger, Norway} % Location
    {Jun. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tasked with planning and developing a new application aimed at youth in Norway.}
        \item {Worked as back-end developer during the internship. Mostly using PHP and the Drupal 8 framework.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Teaching Assistant} % Job title
    {Norwegian University of Science and Technology.} % Organization
    {Gjøvik, Norway} % Location
    {Aug. 2018 - Jun. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching assistant in Fundemental Programming in C++ fall of 2018 and 2019. Worked mainly by supervising and guiding first year students in weekly tasks and during assigments. Also graded assignments and helped students preaparing for exams.}
        \item {Teaching assistant in Object-Oriented Programming in C++ sprint of 2019 and 2020. Worked mainly by supervising and guiding first year students in weekly tasks and during assigments. Also graded assignments and helped students preaparing for exams.}
        \item {Teaching assistant in Algorithmic Methods in C++ sprint fall of 2019. Worked mainly by supervising and guiding second year students in weekly tasks and while preaparing for exams.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Computer Technician \& Customer Support} % Job title
    {Sogn og Fjordane County Municipality} % Organization
    {Leikanger, Norway} % Location
    {Aug. 2015 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintenance taks in the windows server environment, customer support and other technical tasks.}
        \item {Worked here as an apprentice until january 2017. Employed as Computer Technician from january to may.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
