%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Presentation}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Framtidsfylket - Trondheim} % Role
    {Presenter at Framtidsfylket in Trondheim} % Event
    {Trondheim, Norway} % Location
    {March. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced The Western Norway Research Institute.}
        \item {Presented myself, my team, department and the Research areas of The Western Norway Research Institute.}
        \item {Encouraged students from The Norwegian University of Science and Technology to apply}.
      \end{cvitems}
  }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Faglunsj: Bjørn Christian Weinbach - Kunstig intelligens i akademia} % Role
    {Lunch Presentation at the Western Norway University of Applied Sciences} % Event
    {Sogndal, Norway} % Location
    {Feb. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced ChatGPT and Large Language Models.}
        \item {Discussed the challenges with Large Language Models and the future developments of the techology.}
        \item {Responded to questions about AI technologies and related technologies.}.
      \end{cvitems}
    }
%---------------------------------------------------------

%---------------------------------------------------------
  \cventry
    {Speedforsking} % Role
    {Presenter at Speedforsking at Western Norway University of Applied Sciences} % Event
    {Sogndal, Norway} % Location
    {Sep. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Introduced the philosophical definitions of Information and Data.}
        \item {Presented Images as a valid and valuable data source.}
        \item {Discussed the rise of social media and the true value of data.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
